Mega-analysis of the Interoceptive Accuracy Scale (IAS)

### 2025-11-03 analysis/Study1.qmd
minor
updated study 1

df17 <- haven::read_sav("../data/Petzke2024/ETUDE1_main study.sav") |>
  mutate_all(as.numeric) |>
  select(age_to_be_completed_that_year, Gender, starts_with(c("IA0", "PH01")), PHQ_15_total, DIF_total, DDF_total, EOT_total, PHQ_4_total, BPQ_total) |>
  rename(Age= age_to_be_completed_that_year,
         Heart = IA01_01, Hungry = IA01_02, Breathing = IA01_03, Thirsty = IA01_04, Urinate = IA01_05, 
         Defecate=IA01_06, Taste = IA01_07,Vomit = IA01_08, Sneeze = IA01_09, Cough = IA01_10, 
         Temp = IA01_11, Sex_arousal = IA01_12, Wind = IA01_13, Burp = IA01_14,Muscles = IA01_15, 
         Bruise = IA01_16, Pain = IA01_17, Blood_Sugar = IA01_18, Affective_touch = IA01_19, 
         Tickle =IA01_20, Itch = IA01_21,
         TAS_DIF = DIF_total, TAS_DDF =  DDF_total, TAS_EOT = EOT_total,
         PHQ15_Sum = PHQ_15_total,
         PHQ4_Sum = PHQ_4_total,
         BPQ_BodyAwareness = BPQ_total,
          ) |>
  mutate(Gender = case_when(
    Gender == 1 ~ "Male",
    Gender == 2 ~ "Female",
    Gender == 3 ~ "Other"))|>
   mutate(
    Age_code = zap_labels(Age),      # remove SPSS labels, get raw numeric codes
    Age = case_when(
      Age_code == -9 ~ NA_real_,
      TRUE ~ 2024 - (2000 + (21 - Age_code))  # compute actual age
    ))

@@

df17$PHQ4_Depression <- (df17$PH01_01 + df17$PH01_02)/2
df17$PHQ4_Anxiety <- (df17$PH01_03 + df17$PH01_04)/2

@@

- **Sample 1a**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 1, downloaded from OSF, included `r report::report_participants(df1a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 1b**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 6, downloaded from OSF, included `r report::report_participants(df1b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 2**: Data from [Gaggero's(2020)](https://osf.io/5x9sg/) study, downloaded from OSF, included `r report::report_participants(df2[c("Age", "Gender")], age = "Age", sex = NA, gender = "Gender")`.
- **Sample 3**: Data from [Campos's(2022)](https://osf.io/j6ef3) study, downloaded from OSF, included `r report::report_participants(df3, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 4**: Data from [Todd's(2022)]( https://osf.io/ms354/) study, downloaded from OSF, included `r report::report_participants(df4, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 5**: Data from [Arslanova (2022)](https://osf.io/mp3cy/) study, downloaded from OSF, included `r report::report_participants(df5_attention, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 6**: Data from [Brand's(2022)](https://osf.io/xwz6g/) study, downloaded from OSF, included `r report::report_participants(df6, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7a**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7b**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7c**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7c, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 8a**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 8b**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 9**: Data from [VonMohr's(2023)](https://osf.io/7p9u5/) study 3, downloaded from OSF, included `r report::report_participants(df9, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 10**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 11**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df11 , age = "Age", sex = NA, gender = "Gender")`.
- **Sample 12**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df12 , age = "Age", sex = NA, gender = "Gender")`.
- **Sample 13**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df13 , age = "Age", sex = NA, gender = "Gender")`.
- **Sample 14**: Data from [Poerio's(2024)](https://osf.io/49wbv) study , included `r report::report_participants(df14 , age = "Age", sex = NA, gender = "Gender")`
- **Sample 15 **: Data from [Poerio's] study , included `r report::report_participants(df15 , age = "Age", sex = NA, gender = "Gender")`
- **Sample 16 **: Data from [Arjona's] study , included `r report::report_participants(df16 , age = "Age", gender = "Gender")`
- **Sample 17 **: Data from [Petzke's](https://osf.io/seru4) study, downloaded from OSF, included `r report::report_participants(df17, age = "Age", gender = "Gender")`.

>>>>

df17 <- haven::read_sav("../data/Petzke2024/ETUDE1_main study.sav") |>
  mutate_all(as.numeric) |>
  select(age_to_be_completed_that_year, Gender, starts_with(c("IA0", "PH01")), PHQ_15_total, DIF_total, DDF_total, EOT_total, PHQ_4_total, BPQ_total, starts_with("BP01_")) |>
  rename(Age= age_to_be_completed_that_year,
         Heart = IA01_01, Hungry = IA01_02, Breathing = IA01_03, Thirsty = IA01_04, Urinate = IA01_05, 
         Defecate=IA01_06, Taste = IA01_07,Vomit = IA01_08, Sneeze = IA01_09, Cough = IA01_10, 
         Temp = IA01_11, Sex_arousal = IA01_12, Wind = IA01_13, Burp = IA01_14,Muscles = IA01_15, 
         Bruise = IA01_16, Pain = IA01_17, Blood_Sugar = IA01_18, Affective_touch = IA01_19, 
         Tickle =IA01_20, Itch = IA01_21,
         TAS_DIF = DIF_total, TAS_DDF =  DDF_total, TAS_EOT = EOT_total,
         PHQ15_Sum = PHQ_15_total,
         PHQ4_Sum = PHQ_4_total,
         BPQ_BodyAwareness = BPQ_total,
          ) |>
  mutate(Gender = case_when(
    Gender == 1 ~ "Male",
    Gender == 2 ~ "Female",
    Gender == 3 ~ "Other"))|>
   mutate(
    Age_code = zap_labels(Age),      # remove SPSS labels, get raw numeric codes
    Age = case_when(
      Age_code == -9 ~ NA_real_,
      TRUE ~ 2024 - (2000 + (21 - Age_code))  # compute actual age
    ))

# df17$BPQ_BodyAwarenessManual <- rowMeans(df17[, grep("^BP01_", names(df17))], na.rm = TRUE)

@@

df17$PHQ4_Depression <- df17$PH01_01 + df17$PH01_02
df17$PHQ4_Anxiety <- df17$PH01_03 + df17$PH01_04

@@

- **Sample 1a**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 1, downloaded from OSF, included `r report::report_participants(df1a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 1b**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 6, downloaded from OSF, included `r report::report_participants(df1b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 2**: Data from [Gaggero's(2020)](https://osf.io/5x9sg/) study, downloaded from OSF, included `r report::report_participants(df2[c("Age", "Gender")], age = "Age", sex = NA, gender = "Gender")`.
- **Sample 3**: Data from [Campos's(2022)](https://osf.io/j6ef3) study, downloaded from OSF, included `r report::report_participants(df3, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 4**: Data from [Todd's(2022)]( https://osf.io/ms354/) study, downloaded from OSF, included `r report::report_participants(df4, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 5**: Data from [Arslanova (2022)](https://osf.io/mp3cy/) study, downloaded from OSF, included `r report::report_participants(df5_attention, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 6**: Data from [Brand's(2022)](https://osf.io/xwz6g/) study, downloaded from OSF, included `r report::report_participants(df6, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7a**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7b**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7c**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7c, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 8a**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 8b**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 9**: Data from [VonMohr's(2023)](https://osf.io/7p9u5/) study 3, downloaded from OSF, included `r report::report_participants(df9, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 10**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 11**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df11 , age = "Age", sex = NA, gender = "Gender")`.
- **Sample 12**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df12 , age = "Age", sex = NA, gender = "Gender")`.
- **Sample 13**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df13 , age = "Age", sex = NA, gender = "Gender")`.
- **Sample 14**: Data from [Poerio's(2024)](https://osf.io/49wbv) study , included `r report::report_participants(df14 , age = "Age", sex = NA, gender = "Gender")`
- **Sample 15 **: Data from [Poerio's] study , included `r report::report_participants(df15 , age = "Age", sex = NA, gender = "Gender")`
- **Sample 16 **: Data from [Arjona's] study , included `r report::report_participants(df16 , age = "Age", gender = "Gender")`
- **Sample 17 **: Data from [Petzke's (2024)](https://osf.io/seru4) study, downloaded from OSF, included `r report::report_participants(df17, age = "Age", gender = "Gender")`.
